{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Appl_Coef_Func_Ests

	\newpage
	\subsection{Curve Estimates for Chosen Specifications}

@@

	\newpage
	\section{Definitions and Proofs}
	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.

>>>>

	\newpage
	\subsection{Simulation - Coefficient Function Estimates}

@@

	\subsection{Application - Coefficient Function Estimates}
	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/appl\_basis\_expansion.pdf}
			\caption{Basis Expansion Regression}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm2.pdf}
			\caption{2 Functional Principal Components}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm3.pdf}
			\caption{3 Functional Principal Components}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm4.pdf}
			\caption{4 Functional Principal Components}
		\end{minipage}
	\end{figure}

	\section{Definitions and Proofs}
	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.
